\documentclass[apaper,20pt]{article}
\def\labelitemi{$\circ$}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fontawesome5} % for using icons
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx} % for reflecting the phone icon
\definecolor{primaryColor}{RGB}{0, 79, 144}
\newcommand{\colorBoxBlue}[1]{\colorbox[RGB]{0,191,255}{#1}}
\newcommand{\colorBoxMustard}[1]{\colorbox[RGB]{255,187,0}{#1}}
\newcommand{\colorBoxGreen}[1]{\colorbox[RGB]{93,226,60}{#1}}
	
\hypersetup{
    colorlinks=true,
    linkcolor=primaryColor,
    filecolor=magenta,      
    urlcolor= blue,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
\newcommand{\MYhref}[3][primaryColor]{\href{#2}{{\color{#1}#3}}}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1in}


\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}


% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}


\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%


\begin{document}


%----------HEADING-----------------
\begin{center}
    \textbf{\Huge \scshape Nitish Sharma} \\ \vspace{5pt}
    \MYhref{tel:+917087491353}{\reflectbox{\faPhone}\ Phone} \quad  
    \MYhref{https://maps.app.goo.gl/rMSBQRqs4LkHJ8Jf6}{\faMapMarker*\ Chandigarh, India} \\ \vspace{5pt}
    \MYhref{mailto:nitish.sharma1186@gmail.com}{\faEnvelope\ Email} \quad 
    \MYhref{https://github.com/itsnitish22}{\faGithub\ GitHub} \quad 
    \MYhref{https://www.linkedin.com/in/itsnitish22/}{\faLinkedin\ LinkedIn} \quad
    \MYhref{https://twitter.com/itsnitish22}{\faTwitter\ Twitter}    
    
\end{center}




%-----------EXPERIENCE----------------


\section{Experience}
\vspace{2pt}
\resumeSubHeadingListStart

\resumeSubheading
{Visit Health}{Noida $\circ$ On-Site}
{Android Developer}{May 2024 - Present}
\begin{itemize}
    \item {Initiated generalising repetitive code and adopted MVVM Architecture, enhancing feature-specific module segregation and doubling navigation efficiency.}
	\item {Led knowledge-sharing sessions on Epoxy, Data Binding, optimal architecture patterns, and documented the strategy for migrating legacy code to updated frameworks.}
     \item {Identified and resolved rendering lags caused by nested RecyclerViews by migrating to Epoxy Controllers, eliminating lags and flickering, reducing rendering time by 60\%.}
	\item {Built and launched critical features including Online Consultation Chat, Hybrid Labs, In-Place App-\&-Doctor Feedbacks, contributing to user engagement.}
\end{itemize}
\vspace{-3pt}

\resumeSubheading
{GeeksforGeeks}{Noida $\circ$ On-Site}
{Android Developer Intern }{June 2023 - May 2024}
\begin{itemize}
    \item {Led development of key features, including the GfG Jobs Portal, Tool Tips, Community Comments, Anonymous Posting, Account Deletion, Global App Search, Explore Section, SplashScreen API, and Roadmaps, improving user engagement by 25\%.}
    \item {Accelerated cold start time of GfG app by 36\% by identifying and resolving main thread bottlenecks and UI rendering problems.}
	\item {Revamped Discuss Section, reducing LOC by 2x, while improving pagination, leading to a faster comments rendering.}
	\item {Created efficient UIs via Epoxy with two-way data binding, streamlining view variables, and state management reducing bounce back rate by 60\%.}
\end{itemize}
\vspace{-3pt}

\resumeSubheading
{FRND}{Bengaluru $\circ$ Remote}
{Android Developer Intern }{December 2022 - March 2023}
\begin{itemize}
	\item {Refactored code from RxJava to Coroutines \& Kotlin Flows while adhering to Clean Architecture principles.}
    \item {Implemented Domain Logic Segregation into distinct packages and classes, enhancing navigation efficiency by 2x.}
	\item {Utilized SDKs to capture User Events with a focus on optimizing UX using Deeplinks \& Deferred Deeplinks.}
	\item {Facilitated Whale-to-Top User connections with an aim to improve user Engagement/Retention and Revenue.}
\end{itemize}
\vspace{-3pt}

\resumeSubheading
{Finocado by Startup Bay}{Ireland $\circ$ Remote}
{Android Developer Intern }{Feburary 2022 - June 2022}
\begin{itemize}
    \item {Leveraged Firebase for Database, Crashlytics \& Analytics. Optimized application through thorough analysis and refinement.}
	\item {Developed and consumed REST APIs via Retrofit. Used MVVM and Components of Android Jetpack.}
	\item {Built CI/CD Pipeline using Github Actions for deploying the updated app to the testers on Firebase.}
\end{itemize}
\vspace{-3pt}

\resumeSubheading
{GeeksforGeeks}{Noida $\circ$ Remote}
{Technical Content Writer Intern {\MYhref{https://auth.geeksforgeeks.org/user/itsnitish22/articles}{(Profile)}}}{January 2022 - June 2022}
\begin{itemize}
	\item {Developed 10+ quality articles for Geeks For Geeks across the spectrum of Software Development.}
	      \item{Researched about DevOps, Cloud Computing, Android and built understanding of the fields.}
\end{itemize}


% \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------

\vspace{-7pt}

\section{Projects}
\resumeSubHeadingListStart
\vspace{2pt}

\resumeSubheading{\MYhref{https://github.com/itsnitish22/ChatRoomFrontEnd}{Chat Room}}{March 2023 - Present}
{Frontend (Kotlin, MVVM, Clean Architecture), Backend (Node.js, Azure,  WebSockets (Socket.IO))}{}
\begin{itemize}
	\item \textbf {Emphasis:} Proactive pursuit of diving into WebSockets, driving innovative ChatRoom development. 
	      \vspace{-2pt}
	\item \textbf {Features:} A global social platform fostering connections with users worldwide.
	      \begin{itemize}
	      	\item{A WebSocket Backend powered by Node.js, hosted on Azure, providing seamless connections and chat experiences.}
	      	\item{Engaging chat rooms supporting multiple participants, featuring real-time updates on participants joining and leaving events.}
            \item{Coming Soon: Random Chats, Guess Girl or Boy, Guess Streaks, Coin System, and Redeemable Rewards.}
	      \end{itemize}
\end{itemize} 
\vspace{-3pt}

\resumeSubheading{\MYhref{https://github.com/itsnitish22/Sign-Ease}{Sign Ease} {\MYhref[red]{https://play.google.com/store/apps/details?id=com.teamdefine.signease} {[Playstore]}}}{September 2022}
{Android (Kotlin, Coroutines, MVVM, NavGraph, Retrofit, Clean Architecture), Hello Sign, Firebase}{}
\begin{itemize}
	\item \textbf {Problem:} Hostel students Drafting Leaves/ Applications and getting Approvals/ Refusals manually (signatures). 
	\item \textbf {Solution:} A tool that gets your leaves signed from the respective authority or parent/ guardian.
	      \begin{itemize}
	      	\item{Incorporated Hello Sign APIs for catering backend services and dealing with the Signatures.}
	      	\item{Pre-built templates and to-the-point manual details help you choose fast and get your approvals faster.}
            \item{Followed Clean Architecture with MVVM for segregating Domain logic from Data and Views}
	      \end{itemize}
\end{itemize} 
\vspace{20pt}

\resumeSubheading{\MYhref{https://github.com/itsnitish22/Feedback-Prime}{Feedback Prime}}{October 2021}
{Android (Kotlin, Coroutines, MVVM, Retrofit, Symbl.ai, SAWO Labs, APIs)}{}
\begin{itemize}
	\item \textbf {Problem:} Filling survey/feedback forms after every support call.
	      \vspace{-2pt}
	\item \textbf {Solution:} Built an android app for Generating Automated Report of Customer-Executive call.
	      \begin{itemize}
	      	\item{Utilized Async APIs by Symbl.ai which uses Conversation Intelligence for analysing the conversation.}
	      	\item{Followed MVVM Architecture; Used Retrofit;  Recycler View for displaying the generated Report.}
	      \end{itemize}
\end{itemize}
\vspace{-3pt}   

\resumeSubheading{\MYhref{https://github.com/itsnitish22/Suite-Converter}{Suite Converter}}{January 2021}
{Python, Speech Recognition}{}
\begin{itemize}
	\item \textbf {Problem:} Hassle of converting files from one format to another.
	      \vspace{-2pt}
	\item \textbf {Solution:} A one stop easy solution with voice assistant for Major File Conversions.  
	      \begin{itemize}
	      	\item{Used libraries like docx2pdf, pdf2docx, gTTS, SpeechRecognition and pysttx3 for converstion of files.}
	      	\item{Auto detects the Directory Path for keeping the files organised.}
	      \end{itemize}
\end{itemize}
\resumeSubHeadingListEnd
\vspace{0pt}


%-----------SKILLS--------------------


\vspace{-6pt}

\section{Technical Skills}
\resumeSubHeadingListStart
\vspace{2pt}
\resumeSubItem{Languages}{~Kotlin, Java, C++, Python, YAML, JavaScript, Node.js}
\resumeSubItem{Frameworks/Libraries}{~Room, Volley, Retrofit, Firebase, Android Jetpack, SQL, Hilt, Koin, Epoxy, DataBinding, WebSockets}
\resumeSubItem{Tools}{~Git, Android Studio, Postman, Jira Software, GitHub Actions, Docker, Azure, RealmDB}
\resumeSubHeadingListEnd

%-----------Achievements-----------------

\vspace{-3pt}

\section{Achievements}
\begin{itemize}[labelsep=*,label=$\circ$,leftmargin=0.9pc]
	\item {Won 1st Prize for Sponsor's Track in {\MYhref{https://devpost.com/software/feedback-prime-kbg8um}{API World Hackathon}} by Symbl.ai with the Challange - Go Beyond Speech Recognition with Conversation Intelligence APIs.}
 \vspace{-5pt}
     \item {Achieved recognition as a Top-10 Finalist in the batch-wide Soft Skills Communication Competition.}
\vspace{-5pt}
	\item {Attained the badge of {\MYhref{https://badgr.com/public/assertions/DNG85AU6SYWaX6XO5gkoDw?identity__email=nitish.sharma1186@gmail.com}{Postman Student Expert.}}}
\end{itemize}

%-----------EDUCATION-----------------

\vspace{-6pt}

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Chandigarh University}{Mohali, Punjab}
{Bachelor of Engineering - Computer Science;  CGPA: 8.33}{}
\vspace{0pt}
\resumeSubheading
{Govt. Model Sr. Sec School, 37-B}{Chandigarh}
{Secondary School Education (Science);  Percentage: 85.6}{}
\vspace{0pt}
\resumeSubheading
{Stepping Stones Sr. Sec. School, 37-D}{Chandigarh}
{High School Education;  CGPA: 9.2}{}
\resumeSubHeadingListEnd

\end{document}
